---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multiCure

[![Build Status](https://github.com/zhenyu1029/multiCure/workflows/R-CMD-check/badge.svg)](https://github.com/zhenyu1029/multiCure/actions)
[![Codecov test coverage](https://codecov.io/gh/zhenyu1029/multiCure/branch/main/graph/badge.svg)](https://codecov.io/gh/zhenyu1029/multiCure?branch=main)
[![R-CMD-check](https://github.com/zhenyu1029/multiCure/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/zhenyu1029/multiCure/actions/workflows/R-CMD-check.yaml)

The goal of **multiCure** is to provide estimation and hypothesis-testing tools 
for cure rates in multivariate survival data. It supports:

- Two‐sample (paired and independent) Wald‐type tests for comparing cure probabilities  
- \(K\)‐sample Wald tests across multiple groups  
- Covariance‐weighted, simple‐average, and pooled Kaplan–Meier estimators of the overall cure rate  
- Ying–Wei variance adjustments for the pooled Kaplan–Meier curve  

## Installation

You can install the development version of **multiCure** from GitHub with:

```{r}
# install.packages("remotes")  # if you don't already have remotes
remotes::install_github("zhenyu1029/multiCure")
```

Or using **devtools**:

```{r}
# install.packages("devtools")
devtools::install_github("zhenyu1029/multiCure")
```

## Basic Example

```{r}
library(dplyr)
library(multiCure)
library(copula)

# Define data generator
genData2 <- function(n, tau, u_max1, u_max2, p1, p2, cure_time1, cure_time2, k1, k2, missing_prob = 0.1) {
  theta <- copula::iTau(copula::claytonCopula(dim = 2), tau)
  u     <- copula::rCopula(n, copula::claytonCopula(theta, dim = 2))
  u2    <- copula::rCopula(n, copula::claytonCopula(theta, dim = 2))

  t1_u <- (-log(1 - (1 - exp(-cure_time1^k1)) * u[, 1]))^(1 / k1)
  t2_u <- (-log(1 - (1 - exp(-cure_time2^k2)) * u[, 2]))^(1 / k2)

  cured1 <- as.integer(u2[, 1] <= p1)
  cured2 <- as.integer(u2[, 2] <= p2)

  t1 <- ifelse(cured1 == 1, Inf, t1_u)
  t2 <- ifelse(cured2 == 1, Inf, t2_u)

  c1 <- runif(n, 0, u_max1)
  c2 <- runif(n, 0, u_max2)

  o1 <- pmin(t1, c1); d1 <- as.integer(t1 <= c1)
  o2 <- pmin(t2, c2); d2 <- as.integer(t2 <= c2)

  # Introduce missingness
  miss1 <- runif(n) < missing_prob
  miss2 <- runif(n) < missing_prob

  o1[miss1] <- NA; d1[miss1] <- NA
  o2[miss2] <- NA; d2[miss2] <- NA

  data.frame(id = seq_len(n), observed_time_1 = o1, status_1 = d1,
                               observed_time_2 = o2, status_2 = d2)
}

# Simulate two‐sample cure‐rate data
set.seed(123)
df2 <- genData2(
  n            = 200,
  tau          = 0.5,
  u_max1       = 5,
  u_max2       = 6,
  p1           = 0.4,
  p2           = 0.4,
  cure_time1   = 10,
  cure_time2   = 12,
  k1           = 1.5,
  k2           = 2.0,
  missing_prob = 0.05
)

# Pivot to long format
long_df2 <- df2 %>%
  tidyr::pivot_longer(
    cols          = -id,
    names_to      = c(".value", "group"),
    names_pattern = "(observed_time|status)_(\\d)"
  ) %>%
  mutate(group = factor(group, levels = c("1","2"))) %>%
  rename(time = observed_time)

# Paired two‐sample test
two_paired <- test.2.cure(
  long_df2,
  time,
  status,
  group,
  type = "paired"
)
print(two_paired)

# Independent two‐sample test
two_indep <- test.2.cure(
  long_df2,
  time,
  status,
  group,
  type = "indep"
)
print(two_indep)

# K‐sample Wald test (here with 2 groups yields same as independent)
wald_k <- test.k.cure(long_df2, time, status, group)
print(wald_k)

# Estimation of cure rates
estimates <- est.cure(long_df2, time, status, group)
print(estimates)
```

