---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multiCure

[![Build Status](https://github.com/zhenyu1029/multiCure/workflows/R-CMD-check/badge.svg)](https://github.com/zhenyu1029/multiCure/actions)
[![Codecov test coverage](https://codecov.io/gh/zhenyu1029/multiCure/branch/main/graph/badge.svg)](https://codecov.io/gh/zhenyu1029/multiCure?branch=main)
[![R-CMD-check](https://github.com/zhenyu1029/multiCure/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/zhenyu1029/multiCure/actions/workflows/R-CMD-check.yaml)

The goal of **multiCure** is to provide estimation and hypothesis-testing tools 
for cure rates in multivariate survival data. It supports:

- Two‐sample (paired and independent) Wald‐type tests for comparing cure probabilities  
- \(K\)‐sample Wald tests across multiple groups  
- Covariance‐weighted, simple‐average, and pooled Kaplan–Meier estimators of the overall cure rate  
- Ying–Wei variance adjustments for the pooled Kaplan–Meier curve  

## Installation

You can install the development version of **multiCure** from GitHub with:

```{r}
# install.packages("remotes")  # if you don't already have remotes
remotes::install_github("zhenyu1029/multiCure")
```

Or using **devtools**:

```{r}
# install.packages("devtools")
devtools::install_github("zhenyu1029/multiCure")
```

## Basic Example

```{r}
library(dplyr)
library(multiCure)
library(copula)

# Define data generator
genData2_long <- function(n, tau, u_max1, u_max2, p1, p2, cure_time1, cure_time2, k1, k2, missing_prob = 0.1) {
  # Calculate the copula parameter theta from Kendall's tau
  theta <- copula::iTau(copula::claytonCopula(dim = 2), tau)
  
  # Generate U(0,1) variates from a Clayton copula for survival times
  u <- copula::rCopula(n, copula::claytonCopula(theta, dim = 2))
  # Generate U(0,1) variates from a Clayton copula for cure status
  u2 <- copula::rCopula(n, copula::claytonCopula(theta, dim = 2))
  
  # --- Group 1 Calculations ---
  # Inverse transform to get potential event times for non-cured in group 1
  t1_u <- (-log(1 - (1 - exp(-cure_time1^k1)) * u[, 1]))^(1 / k1)
  # Determine cure status for group 1 based on p1
  cured1 <- as.integer(u2[, 1] <= p1)
  # Assign event time: Inf if cured, otherwise t1_u
  t1 <- ifelse(cured1 == 1, Inf, t1_u)
  # Generate censoring times for group 1
  c1 <- runif(n, 0, u_max1)
  # Calculate observed time and status for group 1
  o1 <- pmin(t1, c1)
  d1 <- as.integer(t1 <= c1)
  
  # Introduce missingness for Group 1
  miss1 <- runif(n) < missing_prob
  o1[miss1] <- NA
  d1[miss1] <- NA
  
  # --- Group 2 Calculations ---
  # Inverse transform to get potential event times for non-cured in group 2
  t2_u <- (-log(1 - (1 - exp(-cure_time2^k2)) * u[, 2]))^(1 / k2)
  # Determine cure status for group 2 based on p2
  cured2 <- as.integer(u2[, 2] <= p2)
  # Assign event time: Inf if cured, otherwise t2_u
  t2 <- ifelse(cured2 == 1, Inf, t2_u)
  # Generate censoring times for group 2
  c2 <- runif(n, 0, u_max2)
  # Calculate observed time and status for group 2
  o2 <- pmin(t2, c2)
  d2 <- as.integer(t2 <= c2)
  
  # Introduce missingness for Group 2
  miss2 <- runif(n) < missing_prob
  o2[miss2] <- NA
  d2[miss2] <- NA
  
  # Create data frames for each group
  df_g1 <- data.frame(
    id = seq_len(n),
    group = factor("1", levels = c("1", "2")),
    time = o1,
    status = d1
  )
  
  df_g2 <- data.frame(
    id = seq_len(n),
    group = factor("2", levels = c("1", "2")),
    time = o2,
    status = d2
  )
  
  # Combine the two group data frames into a single long format data frame
  long_df <- rbind(df_g1, df_g2)
  
  return(long_df)
}

# Simulate two‐sample cure‐rate data
set.seed(123)
long_df2 <- genData2_long(
  n = 200,
  tau = 0.5,
  u_max1 = 5,
  u_max2 = 6,
  p1 = 0.4,
  p2 = 0.4,
  cure_time1 = 10,
  cure_time2 = 12,
  k1 = 1.5,
  k2 = 2.0,
  missing_prob = 0.05
)
head(long_df2)

# Paired two‐sample test
two_paired <- test.2.cure(
  long_df2,
  time,
  status,
  group,
  type = "paired"
)
print(two_paired)

# Independent two‐sample test
two_indep <- test.2.cure(
  long_df2,
  time,
  status,
  group,
  type = "indep"
)
print(two_indep)

# K‐sample Wald test (here with 2 groups yields same as independent)
wald_k <- test.k.cure(long_df2, time, status, group)
print(wald_k)

# Estimation of cure rates
estimates <- est.cure(long_df2, time, status, group)
print(estimates)
```

